\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-06 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
  \caption{Distribution of Lianjia's stores' percentage across China}
  \label{fig:precise_proportion_contraction}
  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map. Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores. Additionally, Sansha city is featured in the bottom right corner of the graph.
\end{figure}

@@

To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform based consolidation strategy as an exogenous shock to the market. The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia and attracting various franchise stores to join the network. Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage. The number of

To conduct the

\footnote{According to the IPO prospectus, in year 2021, Lianjia is expected to achive approximately 76\% of cross stores transactions.}

% Accodring to 招股书，链家在2021的成交是cross store占比76\%

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the study background and statistical summary. Section \ref{sec:mechanism_design} presents the main result of our finding. Section \ref{sec:network_effect} presents our measure to the local network effect and analyzes the platform-mediated consolidation on the local network effect. Finally, Section \ref{sec:conclusion} contains the discussion and concludes.

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy. This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's Agent Cooperation Network (ACN) strategy. The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store. By sharing transaction dividends among multiple stores, Lianjia fosters cooperation with other market competitors and integrates their resources to enhance service quality for customers. This approach is designed to improve efficiency and customer satisfaction by combining online and offline resources, thus providing a comprehensive and streamlined service experience.

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
  \caption{Distribution of Lianjia's stores' percentage across China}
  \label{fig:precise_proportion_contraction}
  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map. Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores. Additionally, Sansha city is featured in the bottom right corner of the graph.
\end{figure}

@@

To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-based consolidation strategy as an exogenous shock to the market. This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network. Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage. However, our findings suggest that the platform-based consolidation does not effectively reduce the transaction period nor does it promote price concessions. This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions. While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.

According to Lianjia's IPO prospectus, the company is projected to achieve approximately 76\% of cross-store transactions in 2021. This underscores the necessity of analyzing the network effects among Lianjia's offline stores and conducting a detailed examination of these effects. To assess Lianjia's network effect, we propose a measure of the local network effect by incorporating neighborhoods and offline stores, given that offline stores predominantly cluster around neighborhoods. We employ a Breadth-First Search (BFS) algorithm to construct the network formation and propose a gravity-based measure to evaluate the offline clustered network effect on neighborhoods. Additionally, we examine the impact of online-mediated consolidation on the offline stores' network effect on neighborhoods. Our findings reveal that Lianjia's offline stores exhibit a moderate network effect characterized by local clustering patterns.\footnote{\ref{fig:typical_sample_lianjia} shows a typical observation in Chengdu that two proximate Lianjia stores closely cooperate to manage property listings. In this arrangement, agents have the flexibility to bring customers for house tours.} Furthermore, the platform-mediated consolidation significantly enhances the network effect, indicating that this consolidation strategy effectively strengthens the network effect of Lianjia's offline stores.

The structure of the paper is organized as follows. Section \ref{sec:literature_review} provides a comprehensive review of the relevant literature. Section \ref{sec:data} outlines the study's background, including a statistical summary and stylized facts. Section \ref{sec:mechanism_design} examines the impact of Lianjia's offline store expansion and platform-mediated consolidation on transaction properties.. Section \ref{sec:network_effect} details the measurement of local network effects and analyzes the influence of platform-mediated consolidation on these effects. Finally, Section \ref{sec:conclusion} discusses the findings and offers concluding remarks.

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy. This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's ACN strategy. The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store. By sharing transaction dividends among multiple stores, Lianjia fosters cooperation with other market competitors and integrates their resources to enhance service quality for customers. This approach is designed to improve efficiency and customer satisfaction by combining online and offline resources, thus providing a comprehensive and streamlined service experience.
